%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Analyst}
    {Wavenet}
    {Leuze-en-Hainaut, Belgium}
    {Oct. 2013}
    {
      \begin{cvitems}
        \item Developed components for the DotNetNuke CMS in APS.NET WebForm
        \item Developed components for the Umbraco CMS in ASP.NET MVC
        \item Integrated design in DotNetNuke
        \item Integrated design in Umbraco
        \item Built APS .NET API 
      \end{cvitems}
    }

  \cventry
    {Trainer}
    {Wavenet}
    {Belgium}
    {Oct. 2014 - Mar 2016}
    {
      \begin{cvitems}
        \item Gave training for jobseeker. Topics of those training was C\# development, WinForm, WPF,\\ASP.NET WebForm and MVC, HTML, CSS integration, JavaScript, T-SQL, XNA.
      \end{cvitems}
    }

  \cventry
      {Software Engineer}
      {Magotteaux}
      {Liège, Belgium}
      {Mar. 2016 - Jan. 2019}
      {
        \begin{cvitems}
          \item Developed a web application to manage the company plant production.\\The application used the following technologies: ASP.NET,Knockout.js, SASS and SQL.\\This application also used some SAP services to retrieve the informations.
          \item Developed a web application to allow customer to follow their orders.\\The application used the following technologies: ASP.NET, Vue.js with Typescript,\\SASS, SQL and the Umbraco CMS.\\This application also used some SAP services to retrieve the informations.
        \end{cvitems}
      }

  \cventry
    {Software Engineer}
    {Actiris}
    {Brussel, Belgium}
    {Feb. 2019}
    {
      \begin{cvitems}
        \item Worked on an application to manage evenment of the company. I've worked on the\\front-end of the application with Angular, TypeScript and SASS.
        \item Workd on an application to manage the data of the Active Directory. This application\\was build with C\#, ASP.NET Core for the back-end and Angular for the front-end.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
